Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-19 paper.qmd
Fixed the issue of Figure 7

tsne_two_curvy_scaled <- algo_obj_two_curvy2$nldr_scaled
distance_two_curvy2 <- algo_obj_two_curvy2$distance_df
tr_from_to_df_two_curvy2 <- algo_obj_two_curvy2$tr_from_to_df
benchmark_two_curvy2 <- algo_obj_two_curvy2$benchmark
df_bin_centroids_two_curvy2 <- algo_obj_two_curvy2$df_bin_centroids
df_bin_two_curvy2 <- algo_obj_two_curvy2$df_bin
hex_grid_with_counts_two_curvy2 <- algo_obj_two_curvy2$hex_grid_with_counts

@@

```{r}
#| label: hexbin-regular-two-curvy3
## hexagon binning to have regular hexagons
hb_obj_two_curvy3 <- hex_binning(
  data = tsne_two_curvy_scaled, 
  bin1 = 48, 
  r2 = r2)

a1_3 <- calc_bins_y(
  bin1 = 48, 
  r2 = r2
)$a1

## Data set with all centroids
all_centroids_df3 <- hb_obj_two_curvy3$centroids

## Generate all coordinates of hexagons
hex_grid3 <- hb_obj_two_curvy3$hex_poly

## To obtain the standardise counts within hexbins
counts_df3 <- hb_obj_two_curvy3$std_cts
df_bin_centroids3 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df3, 
  counts_df = counts_df3) |>
  filter(drop_empty == FALSE) |>
  mutate(b1 = "b1 = 14")

boxplot3 <- ggplot(df_bin_centroids3, 
                   aes(x=bin_counts)) + 
    geom_histogram()

hex_grid_with_counts_s_curve3 <- full_join(hex_grid3, 
                                          df_bin_centroids3 |> select(hexID, std_counts), 
                                          by = c("hex_poly_id" = "hexID"))

hex_grid_coloured_two_curvy3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = tsne_two_curvy_scaled,
           aes(x = tSNE1, y = tSNE2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "D") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos, cex = 1.5)
```

>>>>

distance_two_curvy2 <- algo_obj_two_curvy2$distance_df
tr_from_to_df_two_curvy2 <- algo_obj_two_curvy2$tr_from_to_df
benchmark_two_curvy2 <- algo_obj_two_curvy2$benchmark
df_bin_centroids_two_curvy2 <- algo_obj_two_curvy2$df_bin_centroids
df_bin_two_curvy2 <- algo_obj_two_curvy2$df_bin
hex_grid_with_counts_two_curvy2 <- algo_obj_two_curvy2$hex_grid_with_counts

@@

```{r}
#| label: hexbin-regular-two-curvy3

num_bins_x_two_curvy <- 48

algo_obj_two_curvy3 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy,
  col_start = "x")

distance_two_curvy3 <- algo_obj_two_curvy3$distance_df
tr_from_to_df_two_curvy3 <- algo_obj_two_curvy3$tr_from_to_df
benchmark_two_curvy3 <- algo_obj_two_curvy3$benchmark
df_bin_centroids_two_curvy3 <- algo_obj_two_curvy3$df_bin_centroids
df_bin_two_curvy3 <- algo_obj_two_curvy3$df_bin
hex_grid_with_counts_two_curvy3 <- algo_obj_two_curvy3$hex_grid_with_counts

distance_df_small_edges_two_curvy3 <- distance_two_curvy3 |>
  filter(distance < benchmark_two_curvy3)

tr_from_to_df_two_curvy3 <- inner_join(
  tr_from_to_df_two_curvy3, distance_df_small_edges_two_curvy3, 
  by = c("from", "to"))

hex_grid_coloured_two_curvy3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_two_curvy3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = tsne_two_curvy_scaled,
           aes(x = tSNE1, y = tSNE2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "D") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos, cex = 1.5)
```
